Online Multiclass Linear Classification with Bandit Feedback

### 2018-11-13 arxiv-version/main.tex
Add figure

% LaTeX packages
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{fullpage}
\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{natbib}

@@

The examples are said to be \emph{linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 = 1 \; , \\
\label{equation:linear-separability-2}
& \forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; .
\end{align}

The examples are said to be \emph{strongly linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:strong-linear-separability-1}
\forall i \in \{1,2,\dots,K\} \qquad \qquad \norm{w_i}^2 & = 1 \; , \\
\label{equation:strong-linear-separability-2}
\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
\label{equation:strong-linear-separability-3}
\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
\end{align}
\end{definition}

@@

Similarly, if $K=2$ and labeled examples are linearly separable
with a margin $\gamma$ then they are strongly linear separable with margin $??$.
Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1}
and \eqref{equation:linear-separability-2} then \dots

>>>>

% LaTeX packages
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{fullpage}
\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{natbib}
\usepackage{tikz}

% TikZ packages
\usetikzlibrary{arrows}
\usetikzlibrary{backgrounds}
\usetikzlibrary{calc}
\usetikzlibrary{cd}  % commutative diagrams
\usetikzlibrary{intersections}
\usetikzlibrary{patterns}
\usetikzlibrary{shapes}
\usetikzlibrary{through}

@@

The examples are said to be \emph{linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:linear-separability-2}
& \forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; .
\end{align}

The examples are said to be \emph{strongly linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:strong-linear-separability-1}
\forall i \in \{1,2,\dots,K\} \qquad \qquad \norm{w_i}^2 & \le 1 \; , \\
\label{equation:strong-linear-separability-2}
\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
\label{equation:strong-linear-separability-3}
\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
\end{align}
\end{definition}

@@

Similarly, if $K=2$ and labeled examples are linearly separable with a margin
$\gamma$ then they are strongly linearly separable with the same margin
$\gamma$. Indeed, if $w_1, w_2$ satisfy \eqref{equation:linear-separability-1}
and \eqref{equation:linear-separability-2} then $w_1' = w_1 - w_2$ and $w_2' =
w_2 - w_1$ satisfy \eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3}.

However, if $K=3$ there exists a set of labeled examples in an inner product
space that is linearly separable with a positive margin $\gamma$ but it is not
strongly linearly separable for any positive $\gamma$. This is best illustrated
on Figure~\ref{figure:linearly-separable-examples-with-margin}.

\begin{figure}
\begin{center}
\input{figures/linearly-separable-examples-with-margin}
\end{center}
\caption{The figure shows labeled examples in $\R^2$ that are linearly separable with a
positive margin $\gamma$. There are $K=3$ classes. The examples of each class
are colored white, gray and black respectively. All examples lie in the ball of
radius $R$ centered at the origin. However, the examples are \emph{not} strongly
linearly separable for any positive margin $\gamma$.
}
\label{figure:linearly-separable-examples-with-margin}
\end{figure}
